### 2020-09-14 priority-gv.tex
Fixed case environment.
Removed usage of amsthm, thmtools, and thm-restate.
Minor changes.

\subsubsection{Terms}
\[
\begin{array}[t]{lcl}
  \tm{\conf{C}}, \tm{\conf{D}}, \tm{\conf{E}}
  & \coloneqq & \tm{\phi\;M}
    \sep        \tm{\ppar{\conf{C}}{\conf{D}}}
    \sep        \tm{\res{x}{y}{\conf{C}}}
  \\
  \tm{\phi}
  & \coloneqq & \tm{\main}
    \sep        \tm{\child}
  \\
  \tm{V}, \tm{W}
  & \coloneqq & \tm{\lambda x.M}
    \sep        \tm{\unit}
    \sep        \tm{\pair{M}{N}}
    \sep        \tm{\inl{M}}
    \sep        \tm{\inr{M}}
  \\
  \tm{E}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{E\;M}
    \sep        \tm{V\;E} \\
  & \sep      & \tm{\letunit{E}{N}} \\
  & \sep      & \tm{\pair{E}{M}}
    \sep        \tm{\pair{V}{E}}
    \sep        \tm{\letpair{x}{y}{E}{M}} \\
  & \sep      & \tm{\inl{E}}
    \sep        \tm{\inr{E}}
    \sep        \tm{\casesum{E}{x}{M}{y}{N}} \\
  \\
  \tm{\conf{F}}
  & \coloneqq & \tm{\phi\;E}
  \\
  \tm{\conf{G}}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{\ppar{\conf{G}}{\conf{C}}}
    \sep        \tm{\res{x}{y}{\conf{G}}}
\end{array}
\]
\[
\begin{array}{ll}
  \tm{\main}  + \tm{\child} = \tm{\main}
  \\
  \tm{\child} + \tm{\main}  = \tm{\main}
\end{array}
\quad
\begin{array}{ll}
  \tm{\child} + \tm{\child} = \tm{\child}
  \\
  \tm{\main}  + \tm{\main} \; \text{undefined}
\end{array}
\]

@@

\subsection{Metatheory}
\begin{restatable}{theorem}{thmpgvsubjectelaboration}[Subject Elaboration]
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$, $\tm{M}\elabarrow\tm{N}$, and $\ty{T}\elabarrow\ty{U}$,
  then $\tseq[\cs{o}]{\ty{\Gamma}}{N}{U}$.
\end{restatable}

\begin{restatable}{lemma}{lempgvvaluedone}
  \label{lem:value-done}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{V}{T}$, then $\cs{o}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr(\ty{T})$.
\end{restatable}

\begin{restatable}{lemma}{lempgvsubstitution}[Substitution]
  \label{lem:pgv-substitution}
  If $\tseq[\cs{p}]{\ty{\Gamma},\tmty{x}{U'}}{M}{T}$ and $\tseq[\cs{q}]{\ty{\Theta}}{V}{U'}$, then $\tseq[\cs{p}]{\ty{\Gamma},\ty{\Theta}}{\subst{M}{V}{x}}{T}$.
\end{restatable}

\begin{restatable}{theorem}{thmpgvsubjectreductionterms}[Subject Reduction ($\tred$)]
  \label{thm:pgv-subject-reduction-terms}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$ and $\tm{M}\tred\tm{M'}$,
  then $\tseq[\cs{o}]{\ty{\Gamma}}{M'}{T}$.
\end{restatable}

\begin{restatable}{theorem}{thmpgvsubjectcongruence}[Subject Congruence ($\equiv$)]
  \label{thm:pgv-subject-congruence}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\equiv\tm{\conf{C'}}$,
  then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
\end{restatable}

\begin{restatable}{theorem}{thmpgvsubjectreductionconfs}[Subject Reduction ($\cred$)]
  \label{thm:pgv-subject-reduction-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\cred\tm{\conf{C'}}$,
  then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
\end{restatable}

>>>>

\subsubsection{Terms}
\[
\begin{array}[t]{lcl}
  \tm{\conf{C}}, \tm{\conf{D}}, \tm{\conf{E}}
  & \coloneqq & \tm{\phi\;M}
    \sep        \tm{\ppar{\conf{C}}{\conf{D}}}
    \sep        \tm{\res{x}{y}{\conf{C}}}
  \\
  \tm{\phi}
  & \coloneqq & \tm{\main}
    \sep        \tm{\child}
  \\
  \tm{V}, \tm{W}
  & \coloneqq & \tm{\lambda x.M}
    \sep        \tm{\unit}
    \sep        \tm{\pair{M}{N}}
    \sep        \tm{\inl{M}}
    \sep        \tm{\inr{M}}
  \\
  \tm{R}
  & \coloneqq & \tm{\link\;\pair{V}{W}}
    \sep        \tm{\new}
    \sep        \tm{\spawn\;V} \\
  & \sep      & \tm{\send\;\pair{V}{W}}
    \sep        \tm{\recv\;V}
    \sep        \tm{\close\;V}
    \sep        \tm{\wait\;V}
  \\
  \tm{E}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{E\;M}
    \sep        \tm{V\;E} \\
  & \sep      & \tm{\letunit{E}{N}} \\
  & \sep      & \tm{\pair{E}{M}}
    \sep        \tm{\pair{V}{E}}
    \sep        \tm{\letpair{x}{y}{E}{M}} \\
  & \sep      & \tm{\inl{E}}
    \sep        \tm{\inr{E}}
    \sep        \tm{\casesum{E}{x}{M}{y}{N}} \\
  \\
  \tm{\conf{F}}
  & \coloneqq & \tm{\phi\;E}
  \\
  \tm{\conf{G}}
  & \coloneqq & \tm{\hole} \\
  & \sep      & \tm{\ppar{\conf{G}}{\conf{C}}}
    \sep        \tm{\res{x}{y}{\conf{G}}}
\end{array}
\]
\[
\begin{array}{ll}
  \tm{\main}  + \tm{\child} = \tm{\main}
  \\
  \tm{\child} + \tm{\main}  = \tm{\main}
\end{array}
\quad
\begin{array}{ll}
  \tm{\child} + \tm{\child} = \tm{\child}
  \\
  \tm{\main}  + \tm{\main} \; \text{undefined}
\end{array}
\]

@@

\subsection{Metatheory}

\begin{restatablelemma}{lempgvvaluedone}
  \label{lem:pgv-value-done}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{V}{T}$, then $\cs{o}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr(\ty{T})$.
\end{restatablelemma}
\begin{proof}
  By induction on the derivation of $\tseq[\cs{o}]{\ty{\Gamma}}{V}{T}$.
  (Details in \cref{prf:lem-pgv-value-done}.)
\end{proof}

\begin{restatablelemma}{lempgvsubstitution}[Substitution]
  \label{lem:pgv-substitution}
  \hfill\\%newline before theorem statement
  If $\tseq[\cs{p}]{\ty{\Gamma},\tmty{x}{U'}}{M}{T}$ and $\tseq[\cs{q}]{\ty{\Theta}}{V}{U'}$, then $\tseq[\cs{p}]{\ty{\Gamma},\ty{\Theta}}{\subst{M}{V}{x}}{T}$.
\end{restatablelemma}
\begin{proof}
  By induction on the derivation of $\tseq[\cs{p}]{\ty{\Gamma},\tmty{x}{U'}}{M}{T}$. Whenever the contexts in the premises and conclusion differ, we use \cref{lem:pgv-value-done} to prove that the priorities are preserved.
  (Details in \cref{prf:lem-pgv-substitution}.)
\end{proof}

\begin{restatablelemma}{lempgvsubjectreductionterms}[Subject Reduction, $\tred$]
  \label{lem:pgv-subject-reduction-terms}
  \hfill\\%newline before theorem statement
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$ and $\tm{M}\tred\tm{M'}$,
  then $\tseq[\cs{o}]{\ty{\Gamma}}{M'}{T}$.
\end{restatablelemma}
\begin{proof}
  By induction on the derivation of $\tm{M}\tred\tm{M'}$.
  (Details in \cref{prf:lem-pgv-subject-reduction-terms}.)
\end{proof}

\begin{restatablelemma}{lempgvsubjectcongruence}[Subject Congruence, $\equiv$]
  \label{lem:pgv-subject-congruence}
  \hfill\\%newline before theorem statement
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\equiv\tm{\conf{C'}}$,
  then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
\end{restatablelemma}
\begin{proof}
  By induction on the derivation of $\tm{\conf{C}}\equiv\tm{\conf{C'}}$.
  (Details in \cref{prf:lem-pgv-subject-congruence}.)
\end{proof}

\begin{restatabletheorem}{thmpgvsubjectreductionconfs}[Subject Reduction, $\cred$]
  \label{thm:pgv-subject-reduction-confs}
  \hfill\\%newline before theorem statement
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$ and $\tm{\conf{C}}\cred\tm{\conf{C'}}$,
  then $\cseq[\phi]{\ty{\Gamma}}{\conf{C'}}$.
\end{restatabletheorem}
\begin{proof}
  By induction on the derivation of $\tm{\conf{C}}\cred\tm{\conf{C'}}$.
  (Details in \cref{prf:thm-pgv-subject-reduction-confs}.)
\end{proof}

\begin{restatablelemma}{lempgvopenprogressterms}[Open Progress, $\tred$]
  \label{lem:pgv-open-progress-terms}
  If $\tseq[\cs{o}]{\ty{\Gamma}}{M}{T}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    $\tm{M}$ is a value;
  \item[Step]
    There exists some $\tm{N}$ such that $\tm{M}\tred\tm{N}$; or
  \item[Blocked] \label{lem:pgv-progress-terms:blocked}
    There exists some $\tm{E}$ and $\tm{R}$ such that $\tm{M}=\tm{\plug{E}{R}}$.
  \end{description}
\end{restatablelemma}
\begin{proof}
  \todo{Write proof.}
\end{proof}

\begin{restatabletheorem}{thmpgvopenprogressconfs}[Open Progress, $\cred$]
  \label{thm:pgv-open-progress-confs}
  If $\cseq[\phi]{\ty{\Gamma}}{\conf{C}}$, then either:
  \begin{description}[labelwidth=8ex]
  \item[Done]
    There exists some $\tm{V}$ such that $\tm{\conf{C}}=\tm{\main\;V}$;
  \item[Step]
    There exists some $\tm{\conf{D}}$ such that $\tm{\conf{C}} \cred \tm{\conf{D}}$; or
  \item[Blocked]
    There exist $\tm{x_i}$ and $\tm{y_i}$ for $0\leq{i}\leq{n}$, and $\tm{\phi_j}$ and $\tm{R_j}$ for $0\leq{j}\leq{m}$, such that $\tm{\conf{C}}=\tm{\res{x_1y_1\dots x_ny_n}{}{(\phi_1R_1 \parallel\dots\parallel \phi_mR_m)}}$ and for each $\tm{R_j}$ there exists some $\tm{a_j}\in\fn(\ty{\Gamma})$ such that $\blocked(\tm{a_j},\tm{R_j})$.
  \end{description}
\end{restatabletheorem}
\begin{proof}
  \todo{Write proof.}
\end{proof}
